---
title: "Assignment4_10.5&12.6"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tibble)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tidyr)
library(foreign)
```

# 10.5 Exercise

## 1 How can you tell if an object is a tibble? 
##(Hint: try printing mtcars, which is a regular data frame).
```{r}
mtcars
class(mtcars)
class(as_tibble(mtcars))
```

## 2 Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```{r}
#data.frame
df <- data.frame(abc = 1, xyz = "a")

#tibble
tbl <- as.tibble(df)

df$x
tbl$x

df[, "xyz"]
tbl[,"xyz"]

df[, c("abc", "xyz")]
tbl[,c("abc","xyz")]

```
- Difference 1
Using $ a data.frame will partially complete the column. So even though we wrote df$x it returned df$xyz. The advantage is it sometimes can save a few keystrokes, but on the otherside, it can result in accidentally using a different variable than you thought you were using.

- Difference 2
With data.frames, with [ the type of object that is returned differs on the number of columns. If it is one column, it won’t return a data.frame, but instead will return a vector. With more than one column, then it will return a data.frame. 

## 3 If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

df[[var]]

## 4 Practice referring to non-syntactic names in the following data frame by:
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying

#(1)Extracting the variable called 1.
annoying[1]
annoying[["1"]]
annoying$'1'

#(2)Plotting a scatterplot of 1 vs 2.
plot(annoying)
ggplot(annoying, aes(x = `1`, y = `2`)) +geom_point()

#(3)Creating a new column called 3 which is 2 divided by 1.
annoying$`3` <- annoying$`2` / annoying$`1`
annoying[["3"]] <- annoying[["2"]] / annoying[["1"]]


#(4)Renaming the columns to one, two and three.
annoying <- rename(annoying, one = `1`, two = `2`, three = `3`)
glimpse(annoying)
```

## 5 What does tibble::enframe() do? When might you use it?
```{r}
?enframe()
enframe(c(a = 5, b = 7, c=25))

x <- letters[1:3]
enframe(x)

m <- enframe(list(a = 1, b = 2, c=3))
m

n <- enframe(c(a = 1, b = 2,c=3))
n

```
enframe() converts named atomic vectors or lists to two-column data frames. For unnamed vectors, the natural sequence is used as name column.
The advantage is that we can keep the original lists or data frames, but still create tibbles using them. So if I want to keep the backwards compatibility with data frames and list, but still need tibbles, I will use enframe().

## 6 What option controls how many additional column names are printed at the footer of a tibble?
```{r}
?print.tbl_df()
```
The print function for tibbles is in print.tbl_df:
n_extra	: Number of extra columns to print abbreviated information for, if the width is too small for the entire tibble. If NULL, the default, will print information about at most tibble.max_extra_cols extra columns


# 12.6.1 Exercise

```{r}
who

who1 <- who %>%
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases", na.rm = TRUE)
glimpse(who1)
who1

who2 <- who1 %>%
 mutate(key = stringr::str_replace(key, "newrel", "new_rel"))
who2

who3 <- who2 %>%
  separate(key, c("new", "type", "sexage"), sep = "_")
who3

who3 %>%
  count(new)

who4 <- who3 %>%
  select(-new, -iso2, -iso3)

who5 <- who4 %>%
  separate(sexage, c("sex", "age"), sep = 1)
who5
```

##1 In this case study I set na.rm = TRUE just to make it easier to check that we had the correct values. Is this reasonable? Think about how missing values are represented in this dataset. Are there implicit missing values? What’s the difference between an NA and zero?

```{r}
who1 %>%
  filter(cases == 0) %>%
  nrow()
```
Yes, I think it is reasonable. 
Because the rows with the missing values(NA)were redundant as they were not giving any useful information. These missing values may either were inserted explicitily by whoever created the dataset, or they were really missing values. 
The main difference between NA and 0 is that 0 is an actual value indicating that there were no cases of tubercolosis in a country in a given year, whereas a NA value tells us we have no information on the observation at all.

And after we set the na.rm=TRUE to all the data (treat them the same), the explicitly and implicitly missing values are not displayed in who1. And this is reasonable because if we removed all the missing values(including explicitly and implicitly) from the data set, we will have fewer data to analyze. 

##2 What happens if you neglect the mutate() step? (mutate(key = stringr::str_replace(key, "newrel", "new_rel")))
```{r}
who3a <- who1 %>%
  separate(key, c("new", "type", "sexage"), sep = "_")
```
separate causes the warning message saying the values are too few 
```{r}
filter(who3a, new == "newrel") %>% head()
```
if we check the rows for keys beginning with "newrel_", we see that sexage is messing, and type = m014.

##3 I claimed that iso2 and iso3 were redundant with country. Confirm this claim.
```{r}
select(who3, country, iso2, iso3) %>%
  distinct() %>%
  group_by(country) %>%
  filter(n() > 1)
```

##4 For each country, year, and sex compute the total number of cases of TB. Make an informative visualization of the data.
```{r}
who5 %>%
  group_by(country, year, sex) %>%
  filter(year > 1995) %>%
  summarise(cases = sum(cases)) %>%
  unite(country_sex, country, sex, remove = FALSE) %>%
  ggplot(aes(x = year, y = cases, group = country_sex, colour = sex)) +
  geom_line()

```


